---
title: "Demographics Report"
output: html_document
date: '2022-09-12'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Participant characteristics

This table shows participants' demographic characteristics. It will be transferred to Latex and to the manuscript at a later stage.

Note: "From prolific.co https://researcher-help.prolific.co/hc/en-gb/articles/360019238413-Representative-samples-FAQ:

Starting with the youngest allowable participation age on Prolific, we stratify age using five 9-year brackets: 18-27, 28-37, 38-47, 48-57, and 58+. ‘Sex’ is stratified into male and female. ‘Ethnicity (simplified)’ is stratified into the five categories recommended by the UK Office of National Statistics: White, Mixed, Asian, Black and Other."

```{r eval=FALSE, include=FALSE}
library(furniture)
library(tidyverse)

demographics <- read_csv("data/demographics_merged.csv") %>% 
  filter(!is.na(Participant))

length(unique(demographics$Participant))
# Working/school Other (Other (e.g., unemployed, retired))
# Age (years) 18–29 30-49 50-64 65+
# Location of residence 	Town, village, or hamlet 	/ City


df <- read.csv('data/data_pruned_for_analysis_2022-09-14.csv')

demographics <- demographics %>% 
  filter(Participant %in% unique(df$Participant))

demographics <- demographics %>% 
  mutate(
    Employment = if_else(Employment_status %in% c("Full-time", "Part-time") | Student_status == "Yes", "Working/Studying", "Other (e.g., unemployed, retired)"),
    Age_breaks = cut(Age, breaks = c(17.9, 30, 50, 65, 100), labels = c("18–29", "30-49", "50-64", "65+") ),
    Education = if_else(ArchBg == "Yes", "Architecture", if_else(ArtsBg == "Yes", "Arts", "Other")),
    Upbringing_Environment = if_else(tolower(urban_rural_background) == "urban", "Urban", "Other"),
    Current_Environment = if_else(tolower(urban_rural_now) == "urban", "Urban", "Other"),
    Upbringing_Environment = factor(Upbringing_Environment, levels = c("Urban", "Other")),
    Current_Environment = factor(Current_Environment, levels = c("Urban", "Other")),
  )


demographics
table_1 <- demographics  %>% 
  furniture::table1(., splitby = ~ Sex,total = TRUE,
         # Sex,
         Age = Age_breaks,
         Education,
         Ethnicity, 
         "Employment" = Employment, 
         "Upbringing Environment" = `Upbringing_Environment`,
         "Current Environment"= `Current_Environment`,
         "Approval rate" = Approval_rate,
         output = "latex2",
         booktabs = TRUE, caption = "Participant characteristics", label = "tab:participant_characteristics"
        ) 
table_1

write(x = table_1, file = "figures/table_1.tex") 
write(x = table_1, file = "../../../../../../Apps/Overleaf/NICE Online Study/tables/table_1.tex") 

# repeat this without the latex code to print in this document


```
